
This chapter summarises the characteristics of the data and MC samples used in the analyses presented in this dissertation, giving particular attention to the signal and background modelling. The different signals targeted in this dissertation have as common signature a $t\bar{t}$ pair produced in association with $X$, where $X$ is a Higgs boson ($H\to b\bar{b}$) in case of $t\bar{t}H$ production, at least one $Z$ boson ($Z\to \nu \bar{\nu}$) or Higgs boson ($H\to b\bar{b}$) in case of $T\bar{T}$  searches, and a $b\bar{b}$ or a $t\bar{t}$ pair in the case of searches for associated production of heavy Higgs bosons or four-top-quark production. Thus a precise modelling of the main background for those searches, $\ttbar$+jets production, is crucial for these analyses and will be discussed in detail. Given the large mass of the top quark and that the value of $|V_{tb}|$ is very close to 1 ($|V_{tb}| = 1.009\pm0.031$ \cite{Olive:2016xmw}), in the SM it decays almost exclusively into an on-shell $W$ boson and a $b$-quark. A $W$ boson decays in about $1/3$ of the cases into a charged lepton and the corresponding neutrino, with all the three lepton flavours being produced with equal probability. In the remaining cases the $W$ boson decays into a quark-antiquark pair and the relative amount of each combination is determined by the corresponding element in the CKM matrix. As $|V_{cb}|\sim 1.7 \cdot 10^{-3}$ \cite{Olive:2016xmw}, production of $b$-quarks is highly suppressed and the $W$ boson can be considered as a very pure source of light and $c$-quarks: $W^+ \to u\bar{d}$, $c\bar{s}$. The final-state signature of a $t\bar{t}$ event is thus determined by the decay of the two $W$ bosons present in the event: \emph{dilepton} when both $W$ bosons decay leptonically, \emph{lepton+jets} if one $W$ boson decays leptonically and the other one decays hadronically, and \emph{all-hadronic} if both $W$ bosons decay into quarks. The analyses described in this dissertation target the \emph{lepton+jets} and \emph{all-hadronic}+\MET final states, where in the case of signal events the \MET is likely to come from  the presence of high-momentum $Z$ bosons decaying into $\nu \bar{\nu}$ or $W$ bosons decaying leptonically, either to an electron or muon that is not reconstructed, or to a hadronically-decaying $\tau$-lepton that is identified as a jet.
