This glossary describes the naming of nuisance parameters corresponding to various systematic uncertainties in the fit output.
Whenever two names are provided for a given uncertainty, separated by {\sl or}, the first (second) name corresponds to that used in the search discussed in chapter \ref{chp:VLQ} (chapter \ref{chp:ttH}).

\bi
\ib Luminosity: Luminosity
\ib Pileup: Pile-up uncertainty \emph{or} pileup modelling
\ib Electron: 
\bi
\ib identification: Electron ID \emph{or} Electron ID efficiency
\ib reconstruction: Electron reco.
\ib isolation: Electron isol.
\ib energy scale: Electron $E_T$ scale \emph{or} Electron energy scale
\ib energy resolution: Electron $E_T$ resolution \emph{or} Electron energy resolution
\ib trigger: Electron trig. eff.
\ei
\ib Muon:
\bi
\ib identification: Muon ID (stat.), Muon ID (syst.)
\ib reconstruction: Muon TTVA (stat.), Muon TTVA (syst.)
\ib isolation: Muon Isol. (stat.), Muon (syst.)
\ib momentum scale: Muon \pt scale
\ib resolution in the tracker: Muon ID \pt res. \emph{or} Muon energy resolution (ID)
\ib resolution in the muon system: Muon MS \pt res \emph{or} Muon energy resolution (MS)
\ib trigger: Muon Trig. (stat.), Muon ID (syst.)
\ei

\ib Jet vertex tagger: JVT uncertainty \emph{or} Jet vertex tagger efficiency
\ib Jet energy scale:\\ 17 independent components: Effective NP1 \emph{or} JES effective NP 1, Effective NP2 \emph{or} JES effective NP 2, Effective NP3 \emph{or} JES effective NP 3, Effective NP4 \emph{or} JES effective NP 4, Effective NP5 \emph{or} JES effective NP 5, Effective NP6 \emph{or} JES effective NP 6, $\eta$ intercalib. (stat.) \emph{or} JES $\eta$ intercalibration total stat., $\eta$ intercalib. (model) \emph{or} JES $\eta$ intercalibration modelling, $\eta$ intercalib. (non-clos.) \emph{or} JES $\eta$ intercalibration non-closure, Flavour composition \emph{or} JES flavour composition, Flavour response \emph{or} JES flavour response, Pile-up offset mu term \emph{or} JES pileup offset $\mu$, Pile-up offset NPV term \emph{or} JES pileup offset NPV, Pile-up offset \pt term \emph{or} JES pileup offset pT term, $\rho$ topology \emph{or} JES pileup $\rho$ topology, bJES response \emph{or} JES BJES, Punch-through correction

\ib Jet energy resolution: JER \emph{or} Jet energy resolution
\ib Missing transverse momentum: 
\bi
\ib Soft term energy scale: MET TST scale
\ib Soft term resolution: MET TST reso. para. \emph{or} MET soft. reso (para.), MET TST reso. perp. \emph{or} MET soft. reso (perp.)
\ei
\ib $b$-tagging uncertainties:\\ 5 eigenvectors corresponding to $b$-jet \pt bins ordered from the largest to the smallest: b-tag (B) EV1 \emph{or} b-tag Eigenvar. 0, b-tag (B) EV2 \emph{or} b-tag Eigenvar. 1, b-tag (B) EV3 \emph{or} b-tag Eigenvar. 2, b-tag (B) EV4 \emph{or} b-tag Eigenvar. 3, b-tag (B) EV5 \emph{or} b-tag Eigenvar. 4
\ib $c$-tagging uncertainties:\\ 4 eigenvectors corresponding to $c$-jet \pt bins ordered from the largest to the smallest: b-tag (C) EV1 \emph{or} c-tag Eigenvar. 0, b-tag (C) EV2 \emph{or} c-tag Eigenvar. 1, b-tag (C) EV3 \emph{or} c-tag Eigenvar. 2, b-tag (C) EV4 \emph{or} c-tag Eigenvar. 3
\ib light-tagging uncertainties:\\ 14 eigenvectors corresponding to 7 light-jet $p_{T}$ bins and two jet $\eta$ regions ordered from the largest to the smallest: b-tag (L) EV1 \emph{or} l-tag Eigenvar. 0, b-tag (L) EV2 \emph{or} l-tag Eigenvar. 1, b-tag (L) EV3 \emph{or} l-tag Eigenvar. 2, b-tag (L) EV4 \emph{or} l-tag Eigenvar. 3, b-tag (L) EV5 \emph{or} l-tag Eigenvar. 4, b-tag (L) EV6 \emph{or} l-tag Eigenvar. 5, b-tag (L) EV7 \emph{or} l-tag Eigenvar. 6, b-tag (L) EV8 \emph{or} l-tag Eigenvar. 7, b-tag (L) EV9 \emph{or} l-tag Eigenvar. 8, b-tag (L) EV10 \emph{or} l-tag Eigenvar. 9, b-tag (L) EV11 \emph{or} l-tag Eigenvar. 10, b-tag (L) EV12 \emph{or} l-tag Eigenvar. 11, b-tag (L) EV13 \emph{or} l-tag Eigenvar. 12, b-tag (L) EV14 \emph{or} l-tag Eigenvar. 13

\ib high-\pt extrapolation uncertainty for $b$-, $c$- and light-tagging: b-tag extrap. \emph{or} b-tag high pT extrap.
\ib $\tau$-tagging extrapolation: b-tag extrap. from charm \emph{or} b-tag $c\to\tau$ extrap.

\ib $\ttbar$ normalisation:
\bi
\ib $\ttbar$ inclusive cross section: $\ttbar$ inclusive cross section \emph{or} XS $\ttbar$ (inclusive)
\ib $\ttbar+\ge1c$ normalisation: $\ttbar+\ge1c$ norm.
\ei

\ib $\ttbar$ and top $\pt$ NNLO Rw:\\ Uncertainties switching off the NNLO correction for $\ttbar$ and top $\pt$ applied to MC:
\bi
\ib For the search in chapter \ref{chp:VLQ}: $\ttbar$+light NNLO top-$\pt$ correction, $\ttbar+\ge1c$ NNLO top-$\pt$ correction.
\ib For the search in chapter \ref{chp:ttH}: $\ttbar$+light NNLO reweighting pT (tt), $\ttbar$+light NNLO reweighting pT (t), $\ttbar+\ge1c$ NNLO reweighting pT (tt), $\ttbar+\ge1c$ NNLO reweighting pT (t)
\ei 
\ib $\ttbar$+light-jets modelling:
\bi
\ib Radiation model: $\ttbar$+light rad. \emph{or} $\ttbar$+light radiation
\ib Parton shower model: $\ttbar$+light parton shower \emph{or} $\ttbar$+light PS $\&$ hadronisation
\ib Matrix element model: $\ttbar$+light generator \emph{or} $\ttbar$+light NLO generator
\ei
\ib $\ttbar+\ge1c$-jets modelling:
\bi
\ib Radiation model: $\ttbar+\ge1c$ rad. \emph{or} $\ttbar+\ge1c$ radiation
\ib Parton shower model: $\ttbar+\ge1c$ parton shower \emph{or} $\ttbar+\ge1c$ PS $\&$ hadronisation
\ib Matrix element model: $\ttbar+\ge1c$ generator \emph{or} $\ttbar+\ge1c$ NLO generator
\ib NLO modelling in {\sc MG5$\_$aMC} 3F sample: $\ttbar+\ge1c$ NLO reweighting
\ei
\ib $\ttbar+\ge1b$-jets modelling:
\bi
\ib Radiation model: $\ttbar+\ge1b$ rad. (residual) \emph{or} $\ttbar+\ge1b$ radiation (residual)
\ib Parton shower model: $\ttbar+\ge1b$ parton shower (residual) \emph{or} $\ttbar+\ge1b$ PS $\&$ had. (residual)
\ib Matrix element model: $\ttbar+\ge1b$ generator (residual) \emph{or} $\ttbar+\ge1b$ NLO gen. (residual)
\ib NLO modelling in {\sc Sherpa} 4F sample:
\bi
\ib scale variations: $\ttbar+\ge1b$ scale  \emph{or} $\ttbar+\ge1b$ scale choice, $\ttbar+\ge1b$ glosoft  \emph{or} $\ttbar+\ge1b$ global scale, $\ttbar+\ge1b$ Q CMMPS \emph{or} $\ttbar+\ge1b$ Q CMMPS
\ib PDF uncertainties: $\ttbar+\ge1b$ NNPDF  \emph{or} $\ttbar+\ge1b$ NNPDF, $\ttbar+\ge1b$ MSTW \emph{or} $\ttbar+\ge1b$ MSTW PDF
\ib MPI modelling: $\ttbar+\ge1b$ MPI
\ib UE modelling: $\ttbar+\ge1b$ UE modelling
\ei
\ib NLO modelling in {\sc MG5$\_$aMC} 4F sample:
\bi
\ib Parton shower model: $\ttbar+\ge1b$ PS (reweighting) \emph{or} $\ttbar+\ge1b$ PS $\&$ had. (reweighting)
\ib Matrix element model: $\ttbar+\ge1b$ GEN (reweightingl) \emph{or} $\ttbar+\ge1b$ NLO gen. (reweighting)
\ei
\ei
\ib Small backgrounds:
\bi
\ib Multijet uncertainty: QCD norm. \emph{or} Fakes norm.
\ib Diboson cross section uncertainty: Dibosons norm. \emph{or} XS Diboson
\ib $W/Z$+jets cross section uncertainty: V+bjets/cjets/jets norm. \emph{or} W+jets/HF, Z+jets norm.
\ib Single top cross section uncertainty:
\bi
\ib For the search in chapter \ref{chp:VLQ}: Single-top norm. 
\ib For the search in chapter \ref{chp:ttH}: Wt radiation, PS $\&$ hadronisation, diagram subtraction, XS single top (Wt), XS single top (t- $\&$ s-chan)
\ei 
\ib $\ttbar V$ cross section uncertainty: topEW norm. \emph{or} XS ttZ QCD, XS ttZ PDF, ttZ generator, XS ttW QCD, XS ttW PDF, ttW generator 
\ib $\ttbar\ttbar$ cross section uncertainty: SM 4tops norm.
\ib $t\bar{t}H$ modelling:
\bi
\ib For the search in chapter \ref{chp:VLQ} cross section uncertainty: $t\bar{t}H$ norm.
\ib For the search in chapter \ref{chp:ttH} cross section uncertainty, scale choice, parton shower modelling, branching ratio, single tH: XS $t\bar{t}H$ QCD, XS $t\bar{t}H$ PDF, $t\bar{t}H$ scale choice (acceptance), $t\bar{t}H$ PS $\&$ hadronisation, BR($H\to bb$), BR($H\to WW$), BR($H\to other$), XS tHjb QCD, XS tHjbPDF, XS WtH QCD, XS WtH PDF
\ei
\ei


\ei
