\chapter*{Conclusions}
\markboth{Conclusions}{}
\addstarredchapter{Conclusions}

\leavevmode{\parindent=1em\indent} In this dissertation searches for new phenomena involving top quarks and Higgs bosons, with $H\to b\bar{b}$, were presented using 13.2 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}= 13$ \tev, recorded with the ATLAS detector at the LHC. The top quark, together with the Higgs boson, via their special relationship through the large Yukawa coupling ($y_{t}\sim1$), is a perfect tool to probe several BSM scenarios addressing some of the shortcomings of the SM. 
One of the main challenges for the analyses presented is the precise modelling of the main background, $t\bar{t}+\ge1b$ processes, for which no suitable differential measurements are available yet. These analyses required the developments of an improved description of the $t\bar{t}+\ge1b$ process through the implementation of state-of-art MC predictions and a sophisticated model of systematic uncertainties, although this still constitutes the main source of sensitivity degradation. Both analyses presented used a profile likelihood fit exploiting high-statistics control regions to improve the background modelling and reduce the impact of the leading sources of systematic uncertainty.\par
The first analysis presented searched for a variety of signals, including the pair production of a vector-like top quark ($T$) with a significant branching ratio to a top quark and either a SM Higgs boson or a $Z$ boson; four-top-quark production, both within the SM and in several new physics scenarios; and heavy Higgs bosons (neutral and charged) produced in association with, and decaying into, third-generation quarks. The data was analysed in the lepton-plus-jets final state (1-lepton channel) as well as, for the first time, in the jets+$\MET$ final state (0-lepton chennel), characterised by multiple jets and large missing transverse momentum providing a very sensitive and complementary channel. This search profited from the increase in centre-of-mass energy exploiting the high scalar sum of transverse momenta of all final state objects, and the presence of boosted, hadronically-decaying resonances reconstructed as large-radius jets.
No excess over the background expectation was found and 95\% CL upper limits were derived for the different signal benchmark scenarios considered, which are summarised below. \par
For a vector-like singlet (doublet) $T$-quark, a mass below 1020 (1160) $\gev$ is excluded. More generally, a vector-like top partner with a mass below 810 $\gev$ is excluded for any value of the branching ratios into the three decay modes considered.
The 1-lepton channel is also used to set limits on four-top-quark production in different signal benchmark scenarios and on heavy Higgs-boson associated production. In the case of four-top-quark production, a cross section of 15 times the SM prediction is excluded. In the scenario of $\ttbar\ttbar$  production via an EFT model, a cross section of 51 fb is excluded, which translates into $|C_{4t}|/\Lambda^{2} < 2.9$ \tev$^{-2}$. Finally, within the 2UED/RPP model $m_{KK}$ masses below 1.6 $\tev$ are excluded. In the context of a 2HDM within the alignment limit, the $t\bar{t}H(H\to t\bar{t})$ search excludes $\tan\beta$ values below 0.17 (0.11) for $m_{H} = 400$ $\gev$ (1 $\tev$), the $b\bar{b}H(H\to t\bar{t})$ search has insufficient sensitivity to exclude any region of $\tan\beta$, and the $\bar{t}bH^{+}(H^{+}\to t\bar{b})$ search excludes $\tan\beta$ values below 0.65 (0.15) for $m_{H}$ = 200 $\gev$ (1 $\tev$).
In summary, this represents the most sensitive search to date for the well-motivated singlet and doublet vector-like top quark scenarios, providing also the widest coverage in the branching ratio plane, and also the most restrictive bounds on BSM $t\bar{t}t\bar{t}$ production.\par
The second analysis presented aims to measure the cross section for production of the SM Higgs boson in association with a pair of top quarks, from which the top-quark Yukawa coupling can be extracted. Boosted decision trees are employed to reconstruct the event and to discriminate the $t\bar{t}H$ signal from the background. No evidence for the $t\bar{t}H$ process was found, and $95\%$ CL upper limits on the production cross section are set at 3.6 times the SM prediction.  Performing a signal-plus-background fit the signal strength is measured to be $\mu=1.6\pm1.1$.
The combination with the dileptonic channel excludes a signal cross section 4.0 times larger than the SM prediction and yields a best-fit value of $\mu=2.1^{+1.0}_{-0.9}$. This search is one of the most sensitive to date and has already exceeded the Run 1 sensitivity.\par
For all analyses presented in this dissertation a number of future improvements have been identified that should help extend the reach of the BSM searches and aid towards the eventual observation of the $t\bar{t}H$ production mode. At the time of the writing of this dissertation the ATLAS detector has already collected 36 fb$^{-1}$ at $\sqrt{s}=13$ $\tev$ and in the next two years the LHC will deliver $pp$ collisions at the design luminosity providing roughly ten times more data than analysed in this dissertation.
Building on the analysis strategies developed in this dissertation, searches involving top quarks and Higgs boson at the energy frontier will continue to play an important role in providing new insights that may reveal the secrets of the Universe.\\ 

\begin{flushright}

\textit{
The effort to understand the universe\\
is one of the very few things that lifts\\
human life a little above the level of farce,\\
and gives it some of the grace of tragedy.\\
}
S. Weinberg\\


\end{flushright}